%-------------------------
% Resume in LaTeX
% Author : Soundar Murugan (Optimized for Senior Product Engineer Role)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear header/footer
\setlength{\footskip}{4.08003pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine-readable / ATS-friendly
\pdfgentounicode=1

% Simple item macros
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubItem}[2]{\item #1: #2}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://soundarmurugan.com/}{\Large Soundar Murugan}} & Email: \href{mailto:soundarmurugan91@gmail.com}{soundarmurugan91@gmail.com} \\
  \href{https://soundarmurugan.com/}{soundarmurugan.com} & Mobile: \href{tel:+919176870357}{+91-917-687-0357} \\
  Bengaluru, India (Open to remote roles) & \href{https://www.linkedin.com/in/soundarmurugan/}{linkedin.com/in/soundarmurugan} \\
\end{tabular*}

%-----------PROFILE / SUMMARY (WEB + MOBILE)-----------------
\section{Profile}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\multicolumn{2}{p{0.98\textwidth}}{
\small{\raggedright
\textbf{Frontend Engineer (Web \& Mobile)} with nearly 4 years of experience shipping products across \textbf{React.js} and \textbf{React Native}. Specialized in \textbf{Cross-Platform Architecture}, building shared TypeScript SDKs, and optimizing mobile performance (FlashList, Bridge Optimization). Proven track record of improving Mobile NPS by 15\%.
}}
\end{tabular*}

%-----------EXPERIENCE (WEB + MOBILE)-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Candescent (formerly NCR Corporation)}{Bengaluru, India}
    {Software Engineer II}{Apr 2024 -- Present}
    \resumeItemListStart
      \resumeItem{\textbf{Cross-Platform Architecture:} Architected a shared \textbf{TypeScript SDK} used by 5+ internal teams to standardize logic between Web and React Native apps, accelerating feature rollout by \textbf{30\%}.}
      \resumeItem{\textbf{React Native Performance:} Led the "Accelerate Mobile" initiative, optimizing list rendering and transaction flows which directly improved the mobile app's \textbf{NPS by 15\%}.}
      \resumeItem{\textbf{Web UI Modernization:} Spearheaded the migration of the core Transactions module to React + TypeScript, fixing 10+ critical defects and implementing a responsive design system.}
      \resumeItem{\textbf{API Integration Strategy:} Collaborated on the design of a BFF layer to optimize JSON payloads for mobile networks, significantly reducing data usage and latency.}
    \resumeItemListEnd

  \resumeSubheading
    {Candescent (formerly NCR Corporation)}{Bengaluru, India}
    {Software Engineer I}{Jul 2022 -- Mar 2024}
    \resumeItemListStart
      \resumeItem{\textbf{Self-Service Web Portal:} Built a React-based portal used by \textbf{5,000+ users}, implementing complex form handling and responsive layouts for mobile browsers.}
      \resumeItem{\textbf{Chatbot UI:} Enhanced the Chatbot widget for both desktop and mobile web, optimizing animations and touch interactions for a native-like feel.}
      \resumeItem{\textbf{Automation Tooling:} Developed Python scripts to automate client onboarding, reducing manual configuration effort by \textbf{80\%}.}
    \resumeItemListEnd

  \resumeSubheading
    {Factri.AI}{Bengaluru, India}
    {Fullstack Intern}{Feb 2022 -- Jun 2022}
    \resumeItemListStart
      \resumeItem{\textbf{Component Development:} Built a high-performance Table Component with complex sorting and filtering capabilities.}
      \resumeItem{\textbf{Feature Delivery:} Automated QR code generation for 1K+ products and implemented PDF export features.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------AI & OPEN SOURCE PROJECTS-----------------
\section{AI \& Open Source Projects}
\resumeSubHeadingListStart
  \resumeSubItem{\textbf{MCP Server for Mastodon (LLM Agent)}}{Built a backend orchestration layer enabling LLM-driven agents to map natural-language intents to Mastodon API actions using Python.}
  \resumeSubItem{\textbf{Portfolio Site}}{Deployed a personal portfolio site with responsive UI and performance tuning.}
\resumeSubHeadingListEnd

%-----------SKILLS (WEB + MOBILE)-----------------
\section{Skills}
\resumeSubHeadingListStart
  \item \textbf{Frontend}: React, React Native, TypeScript, JavaScript, Tailwind CSS
  \item \textbf{Mobile Specific}: React Navigation, FlatList Optimization, Native Modules, iOS/Android Build Tools
  \item \textbf{State \& Data}: Redux, Context API, REST APIs, JSON Handling
  \item \textbf{Tools}: Git, NPM/Yarn Workspaces, Jest, Flipper (Mobile Debugging)
  \item \textbf{Certifications}: GCP Associate Cloud Engineer
\resumeSubHeadingListEnd

\end{document}
